---
title: "Assignment2"
output: ioslides_presentation
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This shiny app shows the predicted fertility based on the data of Switzerland at about 1888.


## Used model

Linear regression model is used to show the relationship between % of agriculture and fertility.

```{r}
library(stats)
fit1 <- lm(Fertility ~ Agriculture, data = swiss)
```

```{r, eval=FALSE}
predicted <- reactive({
  predict(fit1, newdata = data.frame(Agriculture = input$Agri))
})
```


## User input

A user gives a value of % of males involved in agriculture as occupation using a slide bar.
The value can be from 0 to 100.

## Output plot
50 is used as an input value for demonstration.

```{r, echo=FALSE}
Agri <- 50
plot(swiss$Agriculture, swiss$Fertility, xlab = "% of agriculture", ylab = "Fertility")
abline(fit1, col = "red", lwd = 2)
points(Agri, predict(fit1, newdata = data.frame(Agriculture = Agri)), col = "red", pch = 16, cex = 2)
```


